### 2019-09-30 management.tex
adds dates to milestones

% ===============================================
% This is the hierarchy breakdown
% ===============================================
% \begin{center}
% 	\begin{tikzpicture}[
% 		chair/.style={rectangle, text centered, draw,fill=blue!20, execute at begin node={\begin{varwidth}{9em}},
%    		execute at end node={\end{varwidth}}},
%    		committee/.style={rectangle,draw,fill=green!40, text centered, execute at begin node={\begin{varwidth}{7em}},
%    		execute at end node={\end{varwidth}}},
%    		coordinator/.style={rectangle,draw,fill=red!30, text centered, execute at begin node={\begin{varwidth}{7em}},
%    		execute at end node={\end{varwidth}}},
% 		grandchild/.style={grow=down,xshift=1em,anchor=west,
% 		edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}, execute at begin node={\begin{varwidth}{8em}},
%    		execute at end node={\end{varwidth}}},
% 		first/.style={level distance=12ex},
% 		second/.style={level distance=24ex},
% 		third/.style={level distance=36ex},
% 		level 1/.style={sibling distance=11em}]
% 	    % Parents
% 	    \coordinate
% 	      child[grow=left] {node[chair,anchor=east]{General Co-Chair \\ (Sam Dotson)}}
% 	      child[grow=right] {node[chair,anchor=west]{Technical Co-Chair\\ (Jeremy Mettler)}}
% 	      child[grow=down,level distance=3ex]
% 	    [edge from parent fork down]
% 	    % Children and grandchildren
% 	    child{node[committee] {Non-Technical Subcommittee}
% 	      child[grandchild,first] {node[chair]{Logistics Chair}}
% 	      child[grandchild,second] {node[coordinator]{Hotels and Transportation}}
% 	      child[grandchild,third] {node[coordinator] {Hospitality and Catering}}}
% 	    child {node[committee] {Communications Subcommittee}
% 	      child[grandchild, first] {node[chair] {Publications Chair}}
% 	      child[grandchild, second] {node[coordinator]{Media}}
% 	      child[grandchild, third] {node[coordinator] {Program}}}
% 	    child{node[committee] {Financial Subcommittee}
% 	      child[grandchild,first] {node[chair]{Financial Chair}}
% 	      child[grandchild,second] {node[coordinator]{Registration}}
% 	      child[grandchild,third] {node[coordinator]{Sponsorship}}}
% 	    child {node[committee]{Technical Subcommittee}
% 	      child[grandchild,first] {node[chair]{Sessions Chair}}
% 	      child[grandchild,second] {node[coordinator]{Workshops}}
% 	      child[grandchild,third] {node[coordinator]{Career Fair}}};
% 	\end{tikzpicture}
% \end{center}
\begin{center}
	\begin{tikzpicture}
		\node (gen chair) [chair] {General Co-Chair (Sam Dotson)};
		\node (tech chair) [chair, right of = gen chair, xshift = 5cm] {Technical Co-Chair (Jeremy Mettler)};
		\node (div chair) [chair, left of = gen chair, xshift = -5cm] {Diversity Co-Chair (Nate Reid)};

@@

\subsection{Staffing Requirements}
Staffing for room breakdowns and setups, registration, socials, workshops, tours, etc.  will be supplied by either UIUC ANS members or students of the NPRE department. While it is likely that members of our student chapter will voluntarily fill all the staffing requirements of conference hosted events. If not, we will rely on other student organizations for support including, but not limited to: ACDIS and WIE. Participating in conference events on a staff level is a beneficial experience for any undergraduate who wants to become more familiar with ANS or support their ANS Chapter. Throughout the conference, interacting with registering students, driving groups to tour a scientific facility, and turning rooms for technical sessions provide plentiful opportunities for volunteers to interact with myriad members on a number of levels. Thus, it will be an overall positive experience for the volunteers. Quantitative needs are outlined in Appendix G.

% ===============================================
% Milestones
% ===============================================
\subsection{Milestones}

\begin{center}
\begin{longtable}{c |  c  c}
\hline\hline
Deadline & Task & Responsibility\\
\hline\hline

&November&\\
\hline\hline
& Announcement of 2021 Conference & \\
& Update milestones with lessons learned &\\
& Notify department of selection & Co-Chairs\\
& Confirm Conference Committee & Co-Chairs\\
& Finalize Conference Date & Co-Chairs\\
& Confirm Conference Reservations & Non-Technical\\
& Contact ANS National for support with hotel negotiations& Co-Chairs and Non-Technical\\
& Set up banking through Busey Bank and ANS National& Financial\\
\hline\hline
&December&\\
\hline\hline
&Finalize Facilities Reservations& Non-Technical\\
&Finalize Logo Design& Communications\\
&Begin Designing Website and Social Media& Communications\\
\hline\hline
&$\textbf{2020}$&\\
\hline\hline
&January&\\
\hline\hline
& Finalize meeting schedule& Co-Chairs\\
&&\\
\hline\hline
&February&\\
\hline\hline
& Launch social media plan& Communications\\
&Finalize list of potential speakers& Non-Technical\\
& Finalize technical topics& Technical\\
\hline\hline
&March&\\
\hline\hline
& Contact Speakers and Presenters& Non-Technical and Technical\\
\hline\hline
&April&\\
\hline\hline
& Attend Student Conference at NC State& All\\
& Request lessons learned from NC State& Co-Chairs\\
& Create sponsor letters and contact & General Co-Chair\\
& Prepare tour opportunities& Non-Technical\\
\hline\hline
&May&\\
\hline\hline
& Confirm tours and costs& Non-Technical\\
& Submit Progress Report to SSC& \\
& Create a Call for Papers & Technical and Communications\\
\hline\hline
&June&\\
\hline\hline
& Send Delegates to National Conference& Co-Chairs, All\\
\hline\hline
&July&\\
\hline\hline
& Confirm with all speakers and presenters& \\
& Report on sponsorship& Financial\\
& Reassess budget& Financial\\
\hline\hline
&August&\\
\hline\hline
& Update with sponsors& Financial\\
& Submit second progress to SSC& Co-Chairs\\
\hline\hline
&September&\\
\hline\hline
& Updates on conference deadlines& Financial\\
& Order gift bags& Non-Technical\\
\hline\hline
&October&\\
\hline\hline
& Confirm hotel blocks and contracts& Non-Technical\\
& Registration Opens& Financial\\
& Create and test online paper submission& Technical\\
\hline\hline
&November&\\
\hline\hline
& Attend Winter Conference 2020& Co-Chairs, All\\
& Finalize marketing material& Communications\\
& Report from winter conference & Co-Chairs\\
\hline\hline
&December&\\
\hline\hline
& Update website & Communications \\
& Third progress report to SSC& Co-Chairs\\
& Send out call for papers& Communications\\
\hline\hline
&$\textbf{2021}$&\\
\hline\hline
&January&\\
\hline\hline
& Confirm all judges, panelists, and speakers& Technical\\
& First paper deadline -- send to reviewers & Technical\\
& Recruit student volunteers& All\\
& Finalize tours& Non-Technical\\
& Finalize conference transportation& Non-Technical\\
\hline\hline
&February&\\
\hline\hline
& Finalize program& Communications\\
& Order gift bag items & Financial and Non-Technical\\
& Final Paper Deadline& Technical\\
& Finalize App& Communications\\
& Finalize budget& Financial\\
& Extended Paper Deadline& \\
\hline\hline
&March&\\
\hline\hline
& Print Programs& Communications\\
& Finalize Awards& Technical\\
& Finalize Staff Schedule& Non-Technical\\
& Prepare gift bags, print tags, and banners& Non-Technical\\
& Final progress report to SSC& Co-Chairs\\
\hline\hline
&April&\\
\hline\hline
& Host ANS Student Conference 2021 & \\
& Return seed money& Financial\\
& Process Student Reimbursements& Financial\\
& Finalize financial report& Financial\\
& Submit conference report& Co-Chairs\\
\hline\hline
\end{longtable}
\end{center}

>>>>

% ===============================================
% This is the hierarchy breakdown
% ===============================================
% \begin{center}
% 	\begin{tikzpicture}[
% 		chair/.style={rectangle, text centered, draw,fill=blue!20, execute at begin node={\begin{varwidth}{9em}},
%    		execute at end node={\end{varwidth}}},
%    		committee/.style={rectangle,draw,fill=green!40, text centered, execute at begin node={\begin{varwidth}{7em}},
%    		execute at end node={\end{varwidth}}},
%    		coordinator/.style={rectangle,draw,fill=red!30, text centered, execute at begin node={\begin{varwidth}{7em}},
%    		execute at end node={\end{varwidth}}},
% 		grandchild/.style={grow=down,xshift=1em,anchor=west,
% 		edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}, execute at begin node={\begin{varwidth}{8em}},
%    		execute at end node={\end{varwidth}}},
% 		first/.style={level distance=12ex},
% 		second/.style={level distance=24ex},
% 		third/.style={level distance=36ex},
% 		level 1/.style={sibling distance=11em}]
% 	    % Parents
% 	    \coordinate
% 	      child[grow=left] {node[chair,anchor=east]{General Co-Chair \\ (Sam Dotson)}}
% 	      child[grow=right] {node[chair,anchor=west]{Technical Co-Chair\\ (Jeremy Mettler)}}
% 	      child[grow=down,level distance=3ex]
% 	    [edge from parent fork down]
% 	    % Children and grandchildren
% 	    child{node[committee] {Non-Technical Subcommittee}
% 	      child[grandchild,first] {node[chair]{Logistics Chair}}
% 	      child[grandchild,second] {node[coordinator]{Hotels and Transportation}}
% 	      child[grandchild,third] {node[coordinator] {Hospitality and Catering}}}
% 	    child {node[committee] {Media Subcommittee}
% 	      child[grandchild, first] {node[chair] {Publications Chair}}
% 	      child[grandchild, second] {node[coordinator]{Media}}
% 	      child[grandchild, third] {node[coordinator] {Program}}}
% 	    child{node[committee] {Financial Subcommittee}
% 	      child[grandchild,first] {node[chair]{Financial Chair}}
% 	      child[grandchild,second] {node[coordinator]{Registration}}
% 	      child[grandchild,third] {node[coordinator]{Sponsorship}}}
% 	    child {node[committee]{Technical Subcommittee}
% 	      child[grandchild,first] {node[chair]{Sessions Chair}}
% 	      child[grandchild,second] {node[coordinator]{Workshops}}
% 	      child[grandchild,third] {node[coordinator]{Career Fair}}};
% 	\end{tikzpicture}
% \end{center}
\begin{center}
	\begin{tikzpicture}
		\node (gen chair) [chair] {General Co-Chair (Sam Dotson)};
		\node (tech chair) [chair, right of = gen chair, xshift = 5cm] {Technical Co-Chair (Jeremy Mettler)};
		\node (div chair) [chair, left of = gen chair, xshift = -5cm] {Diversity Co-Chair (Nate Reid)};

@@

\subsection{Staffing Requirements}
Staffing for room breakdowns and setups, registration, socials, workshops, tours, etc.  will be supplied by either UIUC ANS members or students of the NPRE department. While it is likely that members of our student chapter will voluntarily fill all the staffing requirements of conference hosted events. If not, we will rely on other student organizations for support including, but not limited to: ACDIS and WIE. Participating in conference events on a staff level is a beneficial experience for any undergraduate who wants to become more familiar with ANS or support their ANS Chapter. Throughout the conference, interacting with registering students, driving groups to tour a scientific facility, and turning rooms for technical sessions provide plentiful opportunities for volunteers to interact with myriad members on a number of levels. Thus, it will be an overall positive experience for the volunteers. Quantitative needs are outlined in Appendix G on page \pageref{appendix:staff}.

% ===============================================
% Milestones
% ===============================================
\newpage
\subsection{Milestones}

\begin{center}
\begin{longtable}{c |  c  c}
\hline\hline
\textbf{Deadline} & \textbf{Task} & \textbf{Responsible Committee}\\
\hline\hline

&\textbf{November}&\\
\hline\hline
11/21/19 & Announcement of 2021 Conference & \\
11/21/19 & Update milestones with lessons learned &\\
11/21/19 & Notify department of selection & Co-Chairs\\
11/22/19 & Confirm Conference Committee & Co-Chairs\\
11/29/19 & Finalize Conference Date & Co-Chairs\\
\hline\hline
&\textbf{December}&\\
\hline\hline
12/1/19 & Contact ANS National for support with hotel negotiations& Co-Chairs and Non-Technical\\
12/1/19 & Set up banking through Busey Bank and ANS National& Financial\\
12/3/19 & Confirm Conference Reservations & Non-Technical\\
12/3/19 & Finalize Facilities Reservations& Non-Technical\\
12/20/19 & Finalize Logo Design& Media\\
12/20/19 & Begin Designing Website and Social Media& Media\\
\hline\hline
&$\textbf{2020}$&\\
\hline\hline
&\textbf{January}&\\
\hline\hline
1/13/20 & Finalize meeting schedule& Co-Chairs\\
\hline\hline
&\textbf{February}&\\
\hline\hline
2/3/20 & Launch social media plan& Media\\
2/17/20 & Finalize list of potential speakers& Non-Technical\\
2/17/20 & Finalize technical topics& Technical\\
\hline\hline
&\textbf{March}&\\
\hline\hline
3/9/20 & Contact Speakers and Presenters& Non-Technical and Technical\\
3/26-28/20 & Attend Student Conference at NC State& All\\
3/28/20 & Request lessons learned from NC State& Co-Chairs\\
\hline\hline
&\textbf{April}&\\
\hline\hline
4/6/20 & Create sponsor letters and contact & General Co-Chair\\
4/13/20 & Prepare tour opportunities& Non-Technical\\
\hline\hline
&\textbf{May}&\\
\hline\hline
5/4/20 & Confirm tours and costs& Non-Technical\\
5/18/20 & Submit Progress Report to SSC& Co-Chairs\\
5/18/20 & Create a Call for Papers & Technical and Media\\
\hline\hline
&\textbf{June}&\\
\hline\hline
6/7-11/20 & Send Delegates to Annual Meeting in Arizona& Co-Chairs, All\\
\hline\hline
&\textbf{July}&\\
\hline\hline
7/6/20 & Confirm with all speakers and presenters& Technical\\
7/20/20 & Report on sponsorship& Financial\\
7/27/20 & Reassess budget& Financial\\
\hline\hline
&\textbf{August}&\\
\hline\hline
8/10/20 & Update with sponsors& Financial\\
8/24/20 & Submit second progress to SSC& Co-Chairs\\
\hline\hline
&\textbf{September}&\\
\hline\hline
9/14/20 & Updates on conference deadlines& Financial\\
9/21/20 & Finalize gift bag order& Non-Technical\\
\hline\hline
&\textbf{October}&\\
\hline\hline
10/12/20 & Confirm hotel blocks and contracts& Non-Technical\\
10/26/20 & Registration Opens& Financial\\
10/26/20 & Create and test online paper submission& Technical\\
\hline\hline
&\textbf{November}&\\
\hline\hline
11/15-19/20 & Attend Winter Conference 2020 in Chicago& Co-Chairs, All\\
11/24/20 & Finalize marketing material& Media\\
11/24/20 & Report from winter conference & Co-Chairs\\
\hline\hline
&\textbf{December}&\\
\hline\hline
12/4/20 & Reassess Budget & Financial \\
12/4/20 & Update website & Media \\
12/18/20 & Third progress report to SSC& Co-Chairs\\
12/18/20 & Send out call for papers& Media\\
\hline\hline
&$\textbf{2021}$&\\
\hline\hline
&\textbf{January}&\\
\hline\hline
1/4/20 & Confirm all judges, panelists, and speakers& Technical\\
1/18/20 & First paper deadline -- send to reviewers & Technical\\
1/22/20 & Recruit student volunteers& All\\
1/29/21 & Finalize tours& Non-Technical\\
1/29/21& Finalize conference transportation& Non-Technical\\
\hline\hline
&\textbf{February}&\\
\hline\hline
2/1/21 & Finalize program& Media\\
2/1/21 & Order gift bag items & Financial and Non-Technical\\
2/5/21 & Final Paper Deadline& Technical\\
2/9/21 & Extended Paper Deadline& \\
2/15/21 & Finalize Website& Media\\
2/19/21 & Finalize budget& Financial\\
\hline\hline
&\textbf{March}&\\
\hline\hline
3/22/21 & Print Programs& Media\\
3/26/21 & Finalize Awards& Technical\\
3/26/21 & Finalize Staff Schedule& Non-Technical\\
3/29/21 & Final progress report to SSC& Co-Chairs\\
\hline\hline
&\textbf{April}&\\
\hline\hline
4/1/21 & Prepare gift bags, print tags, and banners& Non-Technical\\
4/8-11/21 & Host ANS Student Conference 2021 & \\
4/22/21 & Return seed money& Financial\\
4/29/21 & Process Student Reimbursements& Financial\\
4/29/21 & Finalize financial report& Financial\\
4/29/21 & Submit conference report& Co-Chairs\\
\hline\hline
\end{longtable}
\end{center}
